---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "Erick Yegon "
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the Course Project

This is a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

Instructions:

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

## How to use the application

This is a health center health record app where the patient is asked for details and the patient details are kept in the database for later use to predict the  duration it takes a client to be served in the health facility 
The application is running on (https://ri45rz-erick-yegon.shinyapps.io/Kaptich/?_ga=2.3945392.1831698937.1658718531-1220157865.1658718531)

ui.R, and Server.R Code in my github repository (https://github.com/keyegon/Course-Project-Shiny-Application-and-Reproducible-Pitc)
```{r}
setwd("C:/Users/Erick Yegon/Dropbox/My PC (DESKTOP-1I4SCDT)/Desktop/Kaptich")
```

## Alupe Health Center, Patient Record Database

The data used in the app  is collected by taking patient details 

```{r}
library(tidyverse)
  Alupe <- read_csv("Alupe.csv")

summary(Alupe)

```

## Scatterplot of  Maximum and Minimum Temperatures of Kenyan Cities

```{r}
ggplot(Alupe, aes(Age, Gender, fill= Education))+
  geom_col()+ facet_wrap(~Religion)
```

